---
title: "relationalToE_analysis_p2"
author: "Desmond Ong"
date: "January 4, 2015"
output: html_document
---


```{r preamble, echo=FALSE, message=FALSE}
setwd("~/Dropbox/Stanford/Research/emoResponse/Project/Analysis_relationalToE")
source("~/Dropbox/Stanford/Research/emoResponse/Project/Common R Scripts/processData.R")
#library(poweRlaw)
source("~/Dropbox/Stanford/Research/emoResponse/Project/Common R Scripts/summarySE.R")
library(ggplot2)
library(lme4)
library(plyr)
my_default_theme = theme_bw() + theme(strip.background = element_rect(fill="#FFFFFF"), 
        strip.text = element_text(size=12), 
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=14, vjust=-0.2),
        axis.title.y = element_text(size=14, vjust=0.35),
        legend.text = element_text(size=12),
        title = element_text(size=18, vjust=1),
        panel.grid = element_blank())
```



# disambiguating temporal order from evidence order

https://web.stanford.edu/~dco/experiments/v62


```{r v62-preamble, echo=FALSE, message=FALSE, warning=FALSE}
v62data.wide = read.csv('data_v62.csv', header=TRUE)

v62data <- processData(v62data.wide,
                       variableList = c("order", "askAboutLeftWheelFirst", "showFirstOfPairFirst",
                                        "spinnerPairID", "spinnerPairCode", 
                                        "spinnerID_1","payoff1_1", "payoff2_1", "payoff3_1", 
                                        "prob1_1", "prob2_1", "prob3_1", 
                                        "winChoice_1", "win_1", "winProb_1",
                                        "spinnerID_2","payoff1_2", "payoff2_2", "payoff3_2", 
                                        "prob1_2", "prob2_2", "prob3_2", 
                                        "winChoice_2", "win_2", "winProb_2",
                                        "angleProportion_1", "angleProportion_2",
                                        "attentionCheck1", "attentionCheck2",
                                        "attentionCheck1Time", "attentionCheck2Time",
                                        "reactionTime",
                                        "happy1", "sad1", "content1", "disapp1", "relief1", "regret1",
                                        "happy2", "sad2", "content2", "disapp2", "relief2", "regret2",
                                        "happy3", "sad3", "content3", "disapp3", "relief3", "regret3"), 
                            idVarList = c("workerid", "gender", "age", "showEarlierWheelFirst"),
                            numTrials = 5)
v62data = rename(v62data, c("angleProportion_1"="angleProp_1", "angleProportion_2" = "angleProp_2"))

#again, I messed up the randomization. Here's a fix.

# calculating those who got the attention check correct: i.e. which wheel was rated first.
v62data$attentionCheck1Correct = (v62data$attentionCheck1 - v62data$win_1)==0
v62data$attentionCheck2Correct = (v62data$attentionCheck2 - v62data$win_2)==0

v62data$attentionCheck1TimeCorrect = (v62data$attentionCheck1Time==2 & v62data$showEarlierWheelFirst==0) + (v62data$attentionCheck1Time==10 & v62data$showEarlierWheelFirst==1)
v62data$attentionCheck2TimeCorrect = (v62data$attentionCheck2Time==10 & v62data$showEarlierWheelFirst==0) + (v62data$attentionCheck2Time==2 & v62data$showEarlierWheelFirst==1)

v62data$use = v62data$attentionCheck1Correct & v62data$attentionCheck2Correct & v62data$attentionCheck1TimeCorrect & v62data$attentionCheck2TimeCorrect
# removing those that failed the attention check
# 683 trials passed attention check out of 750: 50 failed, and 17 were NAs (i.e. they wrote stuff or didn't fill it in)
v62data = v62data[v62data$use==TRUE,]; v62data = v62data[!is.na(v62data$use),]

v62data$EV_1 = v62data$prob1_1*v62data$payoff1_1 + v62data$prob2_1*v62data$payoff2_1 + 
  v62data$prob3_1*v62data$payoff3_1
v62data$PE_1 = v62data$win_1 - v62data$EV_1
v62data$absPE_1 = abs(v62data$PE_1)

v62data$EV_2 = v62data$prob1_2*v62data$payoff1_2 + v62data$prob2_2*v62data$payoff2_2 + 
  v62data$prob3_2*v62data$payoff3_2
v62data$PE_2 = v62data$win_2 - v62data$EV_2
v62data$absPE_2 = abs(v62data$PE_2)
```



```{r v62-model-1, echo=FALSE, fig.height=6, fig.width=10}

collapsedDF = data.frame(workerid = c(v62data$workerid, v62data$workerid),
                         askedFirst = c(v62data$askAboutLeftWheelFirst, 1-v62data$askAboutLeftWheelFirst),
                         spinnerID = c(v62data$spinnerID_1, v62data$spinnerID_2),
                         win = c(v62data$win_1, v62data$win_2),
                         PE = c(v62data$PE_1, v62data$PE_2),
                         absPE = c(v62data$absPE_1, v62data$absPE_2),
                         happy = c(v62data$happy1, v62data$happy2),
                         content = c(v62data$content1, v62data$content2),
                         relief = c(v62data$relief1, v62data$relief2),
                         sad = c(v62data$sad1, v62data$sad2),
                         disapp = c(v62data$disapp1, v62data$disapp2),
                         regret = c(v62data$regret1, v62data$regret2))

collapsedModHappy = lmer(happy ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)
collapsedModContent = lmer(content ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)
collapsedModRelief = lmer(relief ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)
collapsedModSad = lmer(sad ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)
collapsedModDisapp = lmer(disapp ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)
collapsedModRegret = lmer(regret ~ (win + PE + absPE) + (1|spinnerID) + (1|workerid), collapsedDF)



```


### Collapsing across all wheels

If we collapse across all wheels (i.e. collapsing left/right, first/second, etc), and just model how Bob feels about that wheel,

* Loss Aversion seems to disappear.

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy, collapsed across all   | `r summary(collapsedModHappy)$coefficients[1,1]` (**`r summary(collapsedModHappy)$coefficients[1,3]`**) | `r summary(collapsedModHappy)$coefficients[2,1]` (**`r summary(collapsedModHappy)$coefficients[2,3]`**)        | `r summary(collapsedModHappy)$coefficients[3,1]` (**`r summary(collapsedModHappy)$coefficients[3,3]`**)       | `r summary(collapsedModHappy)$coefficients[4,1]` (`r summary(collapsedModHappy)$coefficients[4,3]`)
Content, collapsed across all   | `r summary(collapsedModContent)$coefficients[1,1]` (**`r summary(collapsedModContent)$coefficients[1,3]`**) | `r summary(collapsedModContent)$coefficients[2,1]` (**`r summary(collapsedModContent)$coefficients[2,3]`**)        | `r summary(collapsedModContent)$coefficients[3,1]` (**`r summary(collapsedModContent)$coefficients[3,3]`**)       | `r summary(collapsedModContent)$coefficients[4,1]` (`r summary(collapsedModContent)$coefficients[4,3]`)
Relief, collapsed across all   | `r summary(collapsedModRelief)$coefficients[1,1]` (**`r summary(collapsedModRelief)$coefficients[1,3]`**) | `r summary(collapsedModRelief)$coefficients[2,1]` (`r summary(collapsedModRelief)$coefficients[2,3]`)        | `r summary(collapsedModRelief)$coefficients[3,1]` (**`r summary(collapsedModRelief)$coefficients[3,3]`**)       | `r summary(collapsedModRelief)$coefficients[4,1]` (`r summary(collapsedModRelief)$coefficients[4,3]`)
--- | --- | --- | --- | ---
Sad, collapsed across all   | `r summary(collapsedModSad)$coefficients[1,1]` (**`r summary(collapsedModSad)$coefficients[1,3]`**) | `r summary(collapsedModSad)$coefficients[2,1]` (**`r summary(collapsedModSad)$coefficients[2,3]`**)        | `r summary(collapsedModSad)$coefficients[3,1]` (**`r summary(collapsedModSad)$coefficients[3,3]`**)       | `r summary(collapsedModSad)$coefficients[4,1]` (**`r summary(collapsedModSad)$coefficients[4,3]`**)
Disapp, collapsed across all   | `r summary(collapsedModDisapp)$coefficients[1,1]` (**`r summary(collapsedModDisapp)$coefficients[1,3]`**) | `r summary(collapsedModDisapp)$coefficients[2,1]` (**`r summary(collapsedModDisapp)$coefficients[2,3]`**)        | `r summary(collapsedModDisapp)$coefficients[3,1]` (**`r summary(collapsedModDisapp)$coefficients[3,3]`**)       | `r summary(collapsedModDisapp)$coefficients[4,1]` (`r summary(collapsedModDisapp)$coefficients[4,3]`)
Regret, collapsed across all   | `r summary(collapsedModRegret)$coefficients[1,1]` (**`r summary(collapsedModRegret)$coefficients[1,3]`**) | `r summary(collapsedModRegret)$coefficients[2,1]` (**`r summary(collapsedModRegret)$coefficients[2,3]`**)        | `r summary(collapsedModRegret)$coefficients[3,1]` (**`r summary(collapsedModRegret)$coefficients[3,3]`**)       | `r summary(collapsedModRegret)$coefficients[4,1]` (`r summary(collapsedModRegret)$coefficients[4,3]`)

```{r v62-model-2, echo=FALSE, fig.height=6, fig.width=10}

v62data_s1 = subset(v62data, v62data$showEarlierWheelFirst==1)
#v62data_s1 = v62data

firstWheelModHappy   = lmer(happy1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModContent = lmer(content1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModRelief  = lmer(relief1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModSad     = lmer(sad1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModDisapp  = lmer(disapp1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModRegret  = lmer(regret1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)




# summary(firstWheelModHappy)
# summary(firstWheelModContent)
# summary(firstWheelModRelief)
# summary(firstWheelModSad)
# summary(firstWheelModDisapp)
# summary(firstWheelModRegret)


secondWheelModHappy   = lmer(happy2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModContent = lmer(content2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModRelief  = lmer(relief2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModSad     = lmer(sad2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModDisapp  = lmer(disapp2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModRegret  = lmer(regret2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


# summary(secondWheelModHappy)
# summary(secondWheelModContent)
# summary(secondWheelModRelief)
# summary(secondWheelModSad)
# summary(secondWheelModDisapp)
# summary(secondWheelModRegret)


bothWheelModHappy   = lmer(happy3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModContent = lmer(content3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModRelief  = lmer(relief3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModSad     = lmer(sad3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModDisapp  = lmer(disapp3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModRegret  = lmer(regret3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


# summary(bothWheelModHappy)
# summary(bothWheelModContent)
# summary(bothWheelModRelief)
# summary(bothWheelModSad)
# summary(bothWheelModDisapp)
# summary(bothWheelModRegret)



firstWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("First",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(firstWheelModHappy)$coeff[2,1],
                                        summary(firstWheelModHappy)$coeff[3,1],
                                        summary(firstWheelModHappy)$coeff[4,1],
                                        summary(firstWheelModHappy)$coeff[5,1],
                                        summary(firstWheelModHappy)$coeff[6,1],
                                        summary(firstWheelModHappy)$coeff[7,1],
                                        summary(firstWheelModContent)$coeff[2,1],
                                        summary(firstWheelModContent)$coeff[3,1],
                                        summary(firstWheelModContent)$coeff[4,1],
                                        summary(firstWheelModContent)$coeff[5,1],
                                        summary(firstWheelModContent)$coeff[6,1],
                                        summary(firstWheelModContent)$coeff[7,1],
                                        summary(firstWheelModRelief)$coeff[2,1],
                                        summary(firstWheelModRelief)$coeff[3,1],
                                        summary(firstWheelModRelief)$coeff[4,1],
                                        summary(firstWheelModRelief)$coeff[5,1],
                                        summary(firstWheelModRelief)$coeff[6,1],
                                        summary(firstWheelModRelief)$coeff[7,1],
                                        summary(firstWheelModSad)$coeff[2,1],
                                        summary(firstWheelModSad)$coeff[3,1],
                                        summary(firstWheelModSad)$coeff[4,1],
                                        summary(firstWheelModSad)$coeff[5,1],
                                        summary(firstWheelModSad)$coeff[6,1],
                                        summary(firstWheelModSad)$coeff[7,1],
                                        summary(firstWheelModDisapp)$coeff[2,1],
                                        summary(firstWheelModDisapp)$coeff[3,1],
                                        summary(firstWheelModDisapp)$coeff[4,1],
                                        summary(firstWheelModDisapp)$coeff[5,1],
                                        summary(firstWheelModDisapp)$coeff[6,1],
                                        summary(firstWheelModDisapp)$coeff[7,1],
                                        summary(firstWheelModRegret)$coeff[2,1],
                                        summary(firstWheelModRegret)$coeff[3,1],
                                        summary(firstWheelModRegret)$coeff[4,1],
                                        summary(firstWheelModRegret)$coeff[5,1],
                                        summary(firstWheelModRegret)$coeff[6,1],
                                        summary(firstWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(firstWheelModHappy)$coeff[2,2],
                                        summary(firstWheelModHappy)$coeff[3,2],
                                        summary(firstWheelModHappy)$coeff[4,2],
                                        summary(firstWheelModHappy)$coeff[5,2],
                                        summary(firstWheelModHappy)$coeff[6,2],
                                        summary(firstWheelModHappy)$coeff[7,2],
                                        summary(firstWheelModContent)$coeff[2,2],
                                        summary(firstWheelModContent)$coeff[3,2],
                                        summary(firstWheelModContent)$coeff[4,2],
                                        summary(firstWheelModContent)$coeff[5,2],
                                        summary(firstWheelModContent)$coeff[6,2],
                                        summary(firstWheelModContent)$coeff[7,2],
                                        summary(firstWheelModRelief)$coeff[2,2],
                                        summary(firstWheelModRelief)$coeff[3,2],
                                        summary(firstWheelModRelief)$coeff[4,2],
                                        summary(firstWheelModRelief)$coeff[5,2],
                                        summary(firstWheelModRelief)$coeff[6,2],
                                        summary(firstWheelModRelief)$coeff[7,2],
                                        summary(firstWheelModSad)$coeff[2,2],
                                        summary(firstWheelModSad)$coeff[3,2],
                                        summary(firstWheelModSad)$coeff[4,2],
                                        summary(firstWheelModSad)$coeff[5,2],
                                        summary(firstWheelModSad)$coeff[6,2],
                                        summary(firstWheelModSad)$coeff[7,2],
                                        summary(firstWheelModDisapp)$coeff[2,2],
                                        summary(firstWheelModDisapp)$coeff[3,2],
                                        summary(firstWheelModDisapp)$coeff[4,2],
                                        summary(firstWheelModDisapp)$coeff[5,2],
                                        summary(firstWheelModDisapp)$coeff[6,2],
                                        summary(firstWheelModDisapp)$coeff[7,2],
                                        summary(firstWheelModRegret)$coeff[2,2],
                                        summary(firstWheelModRegret)$coeff[3,2],
                                        summary(firstWheelModRegret)$coeff[4,2],
                                        summary(firstWheelModRegret)$coeff[5,2],
                                        summary(firstWheelModRegret)$coeff[6,2],
                                        summary(firstWheelModRegret)$coeff[7,2])
                              )

secondWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("Second",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(secondWheelModHappy)$coeff[2,1],
                                        summary(secondWheelModHappy)$coeff[3,1],
                                        summary(secondWheelModHappy)$coeff[4,1],
                                        summary(secondWheelModHappy)$coeff[5,1],
                                        summary(secondWheelModHappy)$coeff[6,1],
                                        summary(secondWheelModHappy)$coeff[7,1],
                                        summary(secondWheelModContent)$coeff[2,1],
                                        summary(secondWheelModContent)$coeff[3,1],
                                        summary(secondWheelModContent)$coeff[4,1],
                                        summary(secondWheelModContent)$coeff[5,1],
                                        summary(secondWheelModContent)$coeff[6,1],
                                        summary(secondWheelModContent)$coeff[7,1],
                                        summary(secondWheelModRelief)$coeff[2,1],
                                        summary(secondWheelModRelief)$coeff[3,1],
                                        summary(secondWheelModRelief)$coeff[4,1],
                                        summary(secondWheelModRelief)$coeff[5,1],
                                        summary(secondWheelModRelief)$coeff[6,1],
                                        summary(secondWheelModRelief)$coeff[7,1],
                                        summary(secondWheelModSad)$coeff[2,1],
                                        summary(secondWheelModSad)$coeff[3,1],
                                        summary(secondWheelModSad)$coeff[4,1],
                                        summary(secondWheelModSad)$coeff[5,1],
                                        summary(secondWheelModSad)$coeff[6,1],
                                        summary(secondWheelModSad)$coeff[7,1],
                                        summary(secondWheelModDisapp)$coeff[2,1],
                                        summary(secondWheelModDisapp)$coeff[3,1],
                                        summary(secondWheelModDisapp)$coeff[4,1],
                                        summary(secondWheelModDisapp)$coeff[5,1],
                                        summary(secondWheelModDisapp)$coeff[6,1],
                                        summary(secondWheelModDisapp)$coeff[7,1],
                                        summary(secondWheelModRegret)$coeff[2,1],
                                        summary(secondWheelModRegret)$coeff[3,1],
                                        summary(secondWheelModRegret)$coeff[4,1],
                                        summary(secondWheelModRegret)$coeff[5,1],
                                        summary(secondWheelModRegret)$coeff[6,1],
                                        summary(secondWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(secondWheelModHappy)$coeff[2,2],
                                        summary(secondWheelModHappy)$coeff[3,2],
                                        summary(secondWheelModHappy)$coeff[4,2],
                                        summary(secondWheelModHappy)$coeff[5,2],
                                        summary(secondWheelModHappy)$coeff[6,2],
                                        summary(secondWheelModHappy)$coeff[7,2],
                                        summary(secondWheelModContent)$coeff[2,2],
                                        summary(secondWheelModContent)$coeff[3,2],
                                        summary(secondWheelModContent)$coeff[4,2],
                                        summary(secondWheelModContent)$coeff[5,2],
                                        summary(secondWheelModContent)$coeff[6,2],
                                        summary(secondWheelModContent)$coeff[7,2],
                                        summary(secondWheelModRelief)$coeff[2,2],
                                        summary(secondWheelModRelief)$coeff[3,2],
                                        summary(secondWheelModRelief)$coeff[4,2],
                                        summary(secondWheelModRelief)$coeff[5,2],
                                        summary(secondWheelModRelief)$coeff[6,2],
                                        summary(secondWheelModRelief)$coeff[7,2],
                                        summary(secondWheelModSad)$coeff[2,2],
                                        summary(secondWheelModSad)$coeff[3,2],
                                        summary(secondWheelModSad)$coeff[4,2],
                                        summary(secondWheelModSad)$coeff[5,2],
                                        summary(secondWheelModSad)$coeff[6,2],
                                        summary(secondWheelModSad)$coeff[7,2],
                                        summary(secondWheelModDisapp)$coeff[2,2],
                                        summary(secondWheelModDisapp)$coeff[3,2],
                                        summary(secondWheelModDisapp)$coeff[4,2],
                                        summary(secondWheelModDisapp)$coeff[5,2],
                                        summary(secondWheelModDisapp)$coeff[6,2],
                                        summary(secondWheelModDisapp)$coeff[7,2],
                                        summary(secondWheelModRegret)$coeff[2,2],
                                        summary(secondWheelModRegret)$coeff[3,2],
                                        summary(secondWheelModRegret)$coeff[4,2],
                                        summary(secondWheelModRegret)$coeff[5,2],
                                        summary(secondWheelModRegret)$coeff[6,2],
                                        summary(secondWheelModRegret)$coeff[7,2])
                              )


bothWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("Both",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(bothWheelModHappy)$coeff[2,1],
                                        summary(bothWheelModHappy)$coeff[3,1],
                                        summary(bothWheelModHappy)$coeff[4,1],
                                        summary(bothWheelModHappy)$coeff[5,1],
                                        summary(bothWheelModHappy)$coeff[6,1],
                                        summary(bothWheelModHappy)$coeff[7,1],
                                        summary(bothWheelModContent)$coeff[2,1],
                                        summary(bothWheelModContent)$coeff[3,1],
                                        summary(bothWheelModContent)$coeff[4,1],
                                        summary(bothWheelModContent)$coeff[5,1],
                                        summary(bothWheelModContent)$coeff[6,1],
                                        summary(bothWheelModContent)$coeff[7,1],
                                        summary(bothWheelModRelief)$coeff[2,1],
                                        summary(bothWheelModRelief)$coeff[3,1],
                                        summary(bothWheelModRelief)$coeff[4,1],
                                        summary(bothWheelModRelief)$coeff[5,1],
                                        summary(bothWheelModRelief)$coeff[6,1],
                                        summary(bothWheelModRelief)$coeff[7,1],
                                        summary(bothWheelModSad)$coeff[2,1],
                                        summary(bothWheelModSad)$coeff[3,1],
                                        summary(bothWheelModSad)$coeff[4,1],
                                        summary(bothWheelModSad)$coeff[5,1],
                                        summary(bothWheelModSad)$coeff[6,1],
                                        summary(bothWheelModSad)$coeff[7,1],
                                        summary(bothWheelModDisapp)$coeff[2,1],
                                        summary(bothWheelModDisapp)$coeff[3,1],
                                        summary(bothWheelModDisapp)$coeff[4,1],
                                        summary(bothWheelModDisapp)$coeff[5,1],
                                        summary(bothWheelModDisapp)$coeff[6,1],
                                        summary(bothWheelModDisapp)$coeff[7,1],
                                        summary(bothWheelModRegret)$coeff[2,1],
                                        summary(bothWheelModRegret)$coeff[3,1],
                                        summary(bothWheelModRegret)$coeff[4,1],
                                        summary(bothWheelModRegret)$coeff[5,1],
                                        summary(bothWheelModRegret)$coeff[6,1],
                                        summary(bothWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(bothWheelModHappy)$coeff[2,2],
                                        summary(bothWheelModHappy)$coeff[3,2],
                                        summary(bothWheelModHappy)$coeff[4,2],
                                        summary(bothWheelModHappy)$coeff[5,2],
                                        summary(bothWheelModHappy)$coeff[6,2],
                                        summary(bothWheelModHappy)$coeff[7,2],
                                        summary(bothWheelModContent)$coeff[2,2],
                                        summary(bothWheelModContent)$coeff[3,2],
                                        summary(bothWheelModContent)$coeff[4,2],
                                        summary(bothWheelModContent)$coeff[5,2],
                                        summary(bothWheelModContent)$coeff[6,2],
                                        summary(bothWheelModContent)$coeff[7,2],
                                        summary(bothWheelModRelief)$coeff[2,2],
                                        summary(bothWheelModRelief)$coeff[3,2],
                                        summary(bothWheelModRelief)$coeff[4,2],
                                        summary(bothWheelModRelief)$coeff[5,2],
                                        summary(bothWheelModRelief)$coeff[6,2],
                                        summary(bothWheelModRelief)$coeff[7,2],
                                        summary(bothWheelModSad)$coeff[2,2],
                                        summary(bothWheelModSad)$coeff[3,2],
                                        summary(bothWheelModSad)$coeff[4,2],
                                        summary(bothWheelModSad)$coeff[5,2],
                                        summary(bothWheelModSad)$coeff[6,2],
                                        summary(bothWheelModSad)$coeff[7,2],
                                        summary(bothWheelModDisapp)$coeff[2,2],
                                        summary(bothWheelModDisapp)$coeff[3,2],
                                        summary(bothWheelModDisapp)$coeff[4,2],
                                        summary(bothWheelModDisapp)$coeff[5,2],
                                        summary(bothWheelModDisapp)$coeff[6,2],
                                        summary(bothWheelModDisapp)$coeff[7,2],
                                        summary(bothWheelModRegret)$coeff[2,2],
                                        summary(bothWheelModRegret)$coeff[3,2],
                                        summary(bothWheelModRegret)$coeff[4,2],
                                        summary(bothWheelModRegret)$coeff[5,2],
                                        summary(bothWheelModRegret)$coeff[6,2],
                                        summary(bothWheelModRegret)$coeff[7,2])
                              )


wheelModGraphDF = rbind(firstWheelModGraphDF, secondWheelModGraphDF, bothWheelModGraphDF)
wheelModGraphDF$EmotionForWhichWheel = factor(wheelModGraphDF$EmotionForWhichWheel,
                                              levels=c("First", "Second", "Both"))

wheelModGraphDF_earlier = wheelModGraphDF
wheelModGraphDF_earlier$timeOfFirstWheel = "10am"

p1 = ggplot(wheelModGraphDF, aes(x=CoefficientType, fill=FirstWheel, y=Value)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Value-CI, ymax=Value+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  ggtitle("10am wheel shown first") +
  facet_grid(EmotionForWhichWheel ~ Emotion) + xlab("Coeff type") + ylab("Value of coeff") + my_default_theme
```

### Analysis on individual wheels

#### Subset by if earlier wheel is shown first

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy for first wheel, first wheel   | `r summary(firstWheelModHappy)$coefficients[1,1]` (**`r summary(firstWheelModHappy)$coefficients[1,3]`**) | `r summary(firstWheelModHappy)$coefficients[2,1]` (**`r summary(firstWheelModHappy)$coefficients[2,3]`**)        | `r summary(firstWheelModHappy)$coefficients[3,1]` (**`r summary(firstWheelModHappy)$coefficients[3,3]`**)       | `r summary(firstWheelModHappy)$coefficients[4,1]` (`r summary(firstWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModHappy)$coefficients[5,1]` (`r summary(firstWheelModHappy)$coefficients[5,3]`)        | `r summary(firstWheelModHappy)$coefficients[6,1]` (`r summary(firstWheelModHappy)$coefficients[6,3]`)       | `r summary(firstWheelModHappy)$coefficients[7,1]` (`r summary(firstWheelModHappy)$coefficients[7,3]`)
Happy for second wheel, coeffs on first wheel   | `r summary(secondWheelModHappy)$coefficients[1,1]` (**`r summary(secondWheelModHappy)$coefficients[1,3]`**) | `r summary(secondWheelModHappy)$coefficients[2,1]` (`r summary(secondWheelModHappy)$coefficients[2,3]`)        | `r summary(secondWheelModHappy)$coefficients[3,1]` (`r summary(secondWheelModHappy)$coefficients[3,3]`)       | `r summary(secondWheelModHappy)$coefficients[4,1]` (`r summary(secondWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModHappy)$coefficients[5,1]` (**`r summary(secondWheelModHappy)$coefficients[5,3]`**)        | `r summary(secondWheelModHappy)$coefficients[6,1]` (**`r summary(secondWheelModHappy)$coefficients[6,3]`**)       | `r summary(secondWheelModHappy)$coefficients[7,1]` (`r summary(secondWheelModHappy)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Content for first wheel, first wheel   | `r summary(firstWheelModContent)$coefficients[1,1]` (**`r summary(firstWheelModContent)$coefficients[1,3]`**) | `r summary(firstWheelModContent)$coefficients[2,1]` (**`r summary(firstWheelModContent)$coefficients[2,3]`**)        | `r summary(firstWheelModContent)$coefficients[3,1]` (**`r summary(firstWheelModContent)$coefficients[3,3]`**)       | `r summary(firstWheelModContent)$coefficients[4,1]` (`r summary(firstWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModContent)$coefficients[5,1]` (**`r summary(firstWheelModContent)$coefficients[5,3]`**)        | `r summary(firstWheelModContent)$coefficients[6,1]` (`r summary(firstWheelModContent)$coefficients[6,3]`)       | `r summary(firstWheelModContent)$coefficients[7,1]` (`r summary(firstWheelModContent)$coefficients[7,3]`)
Content for second wheel, coeffs on first wheel   | `r summary(secondWheelModContent)$coefficients[1,1]` (**`r summary(secondWheelModContent)$coefficients[1,3]`**) | `r summary(secondWheelModContent)$coefficients[2,1]` (**`r summary(secondWheelModContent)$coefficients[2,3]`**)        | `r summary(secondWheelModContent)$coefficients[3,1]` (`r summary(secondWheelModContent)$coefficients[3,3]`)       | `r summary(secondWheelModContent)$coefficients[4,1]` (`r summary(secondWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModContent)$coefficients[5,1]` (**`r summary(secondWheelModContent)$coefficients[5,3]`**)        | `r summary(secondWheelModContent)$coefficients[6,1]` (**`r summary(secondWheelModContent)$coefficients[6,3]`**)       | `r summary(secondWheelModContent)$coefficients[7,1]` (`r summary(secondWheelModContent)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Relief for first wheel, coeffs on first wheel   | `r summary(firstWheelModRelief)$coefficients[1,1]` (**`r summary(firstWheelModRelief)$coefficients[1,3]`**) | `r summary(firstWheelModRelief)$coefficients[2,1]` (`r summary(firstWheelModRelief)$coefficients[2,3]`)        | `r summary(firstWheelModRelief)$coefficients[3,1]` (**`r summary(firstWheelModRelief)$coefficients[3,3]`**)       | `r summary(firstWheelModRelief)$coefficients[4,1]` (`r summary(firstWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModRelief)$coefficients[5,1]` (`r summary(firstWheelModRelief)$coefficients[5,3]`)        | `r summary(firstWheelModRelief)$coefficients[6,1]` (`r summary(firstWheelModRelief)$coefficients[6,3]`)       | `r summary(firstWheelModRelief)$coefficients[7,1]` (`r summary(firstWheelModRelief)$coefficients[7,3]`)
Relief for second wheel, coeff on first wheel   | `r summary(secondWheelModRelief)$coefficients[1,1]` (**`r summary(secondWheelModRelief)$coefficients[1,3]`**) | `r summary(secondWheelModRelief)$coefficients[2,1]` (`r summary(secondWheelModRelief)$coefficients[2,3]`)        | `r summary(secondWheelModRelief)$coefficients[3,1]` (`r summary(secondWheelModRelief)$coefficients[3,3]`)       | `r summary(secondWheelModRelief)$coefficients[4,1]` (`r summary(secondWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModRelief)$coefficients[5,1]` (`r summary(secondWheelModRelief)$coefficients[5,3]`)        | `r summary(secondWheelModRelief)$coefficients[6,1]` (**`r summary(secondWheelModRelief)$coefficients[6,3]`**)       | `r summary(secondWheelModRelief)$coefficients[7,1]` (`r summary(secondWheelModRelief)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Sad for first wheel, coeffs on first wheel   | `r summary(firstWheelModSad)$coefficients[1,1]` (**`r summary(firstWheelModSad)$coefficients[1,3]`**) | `r summary(firstWheelModSad)$coefficients[2,1]` (**`r summary(firstWheelModSad)$coefficients[2,3]`**)        | `r summary(firstWheelModSad)$coefficients[3,1]` (**`r summary(firstWheelModSad)$coefficients[3,3]`**)       | `r summary(firstWheelModSad)$coefficients[4,1]` (**`r summary(firstWheelModSad)$coefficients[4,3]`**)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModSad)$coefficients[5,1]` (`r summary(firstWheelModSad)$coefficients[5,3]`)        | `r summary(firstWheelModSad)$coefficients[6,1]` (`r summary(firstWheelModSad)$coefficients[6,3]`)       | `r summary(firstWheelModSad)$coefficients[7,1]` (`r summary(firstWheelModSad)$coefficients[7,3]`)
Sad for second wheel, coeff on first wheel   | `r summary(secondWheelModSad)$coefficients[1,1]` (**`r summary(secondWheelModSad)$coefficients[1,3]`**) | `r summary(secondWheelModSad)$coefficients[2,1]` (`r summary(secondWheelModSad)$coefficients[2,3]`)        | `r summary(secondWheelModSad)$coefficients[3,1]` (`r summary(secondWheelModSad)$coefficients[3,3]`)       | `r summary(secondWheelModSad)$coefficients[4,1]` (`r summary(secondWheelModSad)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModSad)$coefficients[5,1]` (**`r summary(secondWheelModSad)$coefficients[5,3]`**)        | `r summary(secondWheelModSad)$coefficients[6,1]` (**`r summary(secondWheelModSad)$coefficients[6,3]`**)       | `r summary(secondWheelModSad)$coefficients[7,1]` (**`r summary(secondWheelModSad)$coefficients[7,3]`**)
--- | --- | --- | --- | ---
Disapp for first wheel, coeffs on first wheel   | `r summary(firstWheelModDisapp)$coefficients[1,1]` (**`r summary(firstWheelModDisapp)$coefficients[1,3]`**) | `r summary(firstWheelModDisapp)$coefficients[2,1]` (`r summary(firstWheelModDisapp)$coefficients[2,3]`)        | `r summary(firstWheelModDisapp)$coefficients[3,1]` (**`r summary(firstWheelModDisapp)$coefficients[3,3]`**)       | `r summary(firstWheelModDisapp)$coefficients[4,1]` (**`r summary(firstWheelModDisapp)$coefficients[4,3]`**)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModDisapp)$coefficients[5,1]` (`r summary(firstWheelModDisapp)$coefficients[5,3]`)        | `r summary(firstWheelModDisapp)$coefficients[6,1]` (`r summary(firstWheelModDisapp)$coefficients[6,3]`)       | `r summary(firstWheelModDisapp)$coefficients[7,1]` (`r summary(firstWheelModDisapp)$coefficients[7,3]`)
Disapp for second wheel, coeff on first wheel   | `r summary(secondWheelModDisapp)$coefficients[1,1]` (**`r summary(secondWheelModDisapp)$coefficients[1,3]`**) | `r summary(secondWheelModDisapp)$coefficients[2,1]` (`r summary(secondWheelModDisapp)$coefficients[2,3]`)        | `r summary(secondWheelModDisapp)$coefficients[3,1]` (`r summary(secondWheelModDisapp)$coefficients[3,3]`)       | `r summary(secondWheelModDisapp)$coefficients[4,1]` (`r summary(secondWheelModDisapp)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModDisapp)$coefficients[5,1]` (**`r summary(secondWheelModDisapp)$coefficients[5,3]`**)        | `r summary(secondWheelModDisapp)$coefficients[6,1]` (**`r summary(secondWheelModDisapp)$coefficients[6,3]`**)       | `r summary(secondWheelModDisapp)$coefficients[7,1]` (`r summary(secondWheelModDisapp)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Regret for first wheel, first wheel   | `r summary(firstWheelModRegret)$coefficients[1,1]` (**`r summary(firstWheelModRegret)$coefficients[1,3]`**) | `r summary(firstWheelModRegret)$coefficients[2,1]` (`r summary(firstWheelModRegret)$coefficients[2,3]`)        | `r summary(firstWheelModRegret)$coefficients[3,1]` (**`r summary(firstWheelModRegret)$coefficients[3,3]`**)       | `r summary(firstWheelModRegret)$coefficients[4,1]` (`r summary(firstWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModRegret)$coefficients[5,1]` (`r summary(firstWheelModRegret)$coefficients[5,3]`)        | `r summary(firstWheelModRegret)$coefficients[6,1]` (`r summary(firstWheelModRegret)$coefficients[6,3]`)       | `r summary(firstWheelModRegret)$coefficients[7,1]` (`r summary(firstWheelModRegret)$coefficients[7,3]`)
Regret for second wheel, coeff on first wheel   | `r summary(secondWheelModRegret)$coefficients[1,1]` (**`r summary(secondWheelModRegret)$coefficients[1,3]`**) | `r summary(secondWheelModRegret)$coefficients[2,1]` (`r summary(secondWheelModRegret)$coefficients[2,3]`)        | `r summary(secondWheelModRegret)$coefficients[3,1]` (`r summary(secondWheelModRegret)$coefficients[3,3]`)       | `r summary(secondWheelModRegret)$coefficients[4,1]` (`r summary(secondWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModRegret)$coefficients[5,1]` (**`r summary(secondWheelModRegret)$coefficients[5,3]`**)        | `r summary(secondWheelModRegret)$coefficients[6,1]` (**`r summary(secondWheelModRegret)$coefficients[6,3]`**)       | `r summary(secondWheelModRegret)$coefficients[7,1]` (`r summary(secondWheelModRegret)$coefficients[7,3]`)







### Overall emotion

#### earlier wheel shown first

If we now look at the overall emotion attributed

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy overall, coeffs on first wheel   | `r summary(bothWheelModHappy)$coefficients[1,1]` (**`r summary(bothWheelModHappy)$coefficients[1,3]`**) | `r summary(bothWheelModHappy)$coefficients[2,1]` (**`r summary(bothWheelModHappy)$coefficients[2,3]`**)        | `r summary(bothWheelModHappy)$coefficients[3,1]` (`r summary(bothWheelModHappy)$coefficients[3,3]`)       | `r summary(bothWheelModHappy)$coefficients[4,1]` (`r summary(bothWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModHappy)$coefficients[5,1]` (**`r summary(bothWheelModHappy)$coefficients[5,3]`**)        | `r summary(bothWheelModHappy)$coefficients[6,1]` (**`r summary(bothWheelModHappy)$coefficients[6,3]`**)       | `r summary(bothWheelModHappy)$coefficients[7,1]` (`r summary(bothWheelModHappy)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Content overall, coeffs on first wheel   | `r summary(bothWheelModContent)$coefficients[1,1]` (**`r summary(bothWheelModContent)$coefficients[1,3]`**) | `r summary(bothWheelModContent)$coefficients[2,1]` (**`r summary(bothWheelModContent)$coefficients[2,3]`**)        | `r summary(bothWheelModContent)$coefficients[3,1]` (`r summary(bothWheelModContent)$coefficients[3,3]`)       | `r summary(bothWheelModContent)$coefficients[4,1]` (`r summary(bothWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModContent)$coefficients[5,1]` (**`r summary(bothWheelModContent)$coefficients[5,3]`**)        | `r summary(bothWheelModContent)$coefficients[6,1]` (**`r summary(bothWheelModContent)$coefficients[6,3]`**)       | `r summary(bothWheelModContent)$coefficients[7,1]` (`r summary(bothWheelModContent)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Relief overall, coeffs on first wheel   | `r summary(bothWheelModRelief)$coefficients[1,1]` (**`r summary(bothWheelModRelief)$coefficients[1,3]`**) | `r summary(bothWheelModRelief)$coefficients[2,1]` (**`r summary(bothWheelModRelief)$coefficients[2,3]`**)        | `r summary(bothWheelModRelief)$coefficients[3,1]` (`r summary(bothWheelModRelief)$coefficients[3,3]`)       | `r summary(bothWheelModRelief)$coefficients[4,1]` (`r summary(bothWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModRelief)$coefficients[5,1]` (`r summary(bothWheelModRelief)$coefficients[5,3]`)        | `r summary(bothWheelModRelief)$coefficients[6,1]` (**`r summary(bothWheelModRelief)$coefficients[6,3]`**)       | `r summary(bothWheelModRelief)$coefficients[7,1]` (`r summary(bothWheelModRelief)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Sad overall, coeffs on first wheel   | `r summary(bothWheelModSad)$coefficients[1,1]` (**`r summary(bothWheelModSad)$coefficients[1,3]`**) | `r summary(bothWheelModSad)$coefficients[2,1]` (**`r summary(bothWheelModSad)$coefficients[2,3]`**)        | `r summary(bothWheelModSad)$coefficients[3,1]` (`r summary(bothWheelModSad)$coefficients[3,3]`)       | `r summary(bothWheelModSad)$coefficients[4,1]` (`r summary(bothWheelModSad)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModSad)$coefficients[5,1]` (**`r summary(bothWheelModSad)$coefficients[5,3]`**)        | `r summary(bothWheelModSad)$coefficients[6,1]` (`r summary(bothWheelModSad)$coefficients[6,3]`)       | `r summary(bothWheelModSad)$coefficients[7,1]` (`r summary(bothWheelModSad)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Regret overall, coeffs on first wheel   | `r summary(bothWheelModRegret)$coefficients[1,1]` (**`r summary(bothWheelModRegret)$coefficients[1,3]`**) | `r summary(bothWheelModRegret)$coefficients[2,1]` (**`r summary(bothWheelModRegret)$coefficients[2,3]`**)        | `r summary(bothWheelModRegret)$coefficients[3,1]` (`r summary(bothWheelModRegret)$coefficients[3,3]`)       | `r summary(bothWheelModRegret)$coefficients[4,1]` (`r summary(bothWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModRegret)$coefficients[5,1]` (**`r summary(bothWheelModRegret)$coefficients[5,3]`**)        | `r summary(bothWheelModRegret)$coefficients[6,1]` (`r summary(bothWheelModRegret)$coefficients[6,3]`)       | `r summary(bothWheelModRegret)$coefficients[7,1]` (`r summary(bothWheelModRegret)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Disapp overall, coeffs on first wheel   | `r summary(bothWheelModDisapp)$coefficients[1,1]` (**`r summary(bothWheelModDisapp)$coefficients[1,3]`**) | `r summary(bothWheelModDisapp)$coefficients[2,1]` (**`r summary(bothWheelModDisapp)$coefficients[2,3]`**)        | `r summary(bothWheelModDisapp)$coefficients[3,1]` (`r summary(bothWheelModDisapp)$coefficients[3,3]`)       | `r summary(bothWheelModDisapp)$coefficients[4,1]` (`r summary(bothWheelModDisapp)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModDisapp)$coefficients[5,1]` (**`r summary(bothWheelModDisapp)$coefficients[5,3]`**)        | `r summary(bothWheelModDisapp)$coefficients[6,1]` (`r summary(bothWheelModDisapp)$coefficients[6,3]`)       | `r summary(bothWheelModDisapp)$coefficients[7,1]` (`r summary(bothWheelModDisapp)$coefficients[7,3]`)

```{r v62-model-3, echo=FALSE, fig.height=6, fig.width=10}

v62data_s1 = subset(v62data, v62data$showEarlierWheelFirst==0)

firstWheelModHappy   = lmer(happy1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModContent = lmer(content1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModRelief  = lmer(relief1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModSad     = lmer(sad1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModDisapp  = lmer(disapp1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
firstWheelModRegret  = lmer(regret1 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


# summary(firstWheelModHappy)
# summary(firstWheelModContent)
# summary(firstWheelModRelief)
# summary(firstWheelModSad)
# summary(firstWheelModDisapp)
# summary(firstWheelModRegret)


secondWheelModHappy   = lmer(happy2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModContent = lmer(content2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModRelief  = lmer(relief2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModSad     = lmer(sad2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModDisapp  = lmer(disapp2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
secondWheelModRegret  = lmer(regret2 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


# summary(secondWheelModHappy)
# summary(secondWheelModContent)
# summary(secondWheelModRelief)
# summary(secondWheelModSad)
# summary(secondWheelModDisapp)
# summary(secondWheelModRegret)


bothWheelModHappy   = lmer(happy3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModContent = lmer(content3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModRelief  = lmer(relief3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModSad     = lmer(sad3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModDisapp  = lmer(disapp3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
bothWheelModRegret  = lmer(regret3 ~ (win_1 + PE_1 + absPE_1) + (win_2 + PE_2 + absPE_2) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


# summary(bothWheelModHappy)
# summary(bothWheelModContent)
# summary(bothWheelModRelief)
# summary(bothWheelModSad)
# summary(bothWheelModDisapp)
# summary(bothWheelModRegret)

firstWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("First",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(firstWheelModHappy)$coeff[2,1],
                                        summary(firstWheelModHappy)$coeff[3,1],
                                        summary(firstWheelModHappy)$coeff[4,1],
                                        summary(firstWheelModHappy)$coeff[5,1],
                                        summary(firstWheelModHappy)$coeff[6,1],
                                        summary(firstWheelModHappy)$coeff[7,1],
                                        summary(firstWheelModContent)$coeff[2,1],
                                        summary(firstWheelModContent)$coeff[3,1],
                                        summary(firstWheelModContent)$coeff[4,1],
                                        summary(firstWheelModContent)$coeff[5,1],
                                        summary(firstWheelModContent)$coeff[6,1],
                                        summary(firstWheelModContent)$coeff[7,1],
                                        summary(firstWheelModRelief)$coeff[2,1],
                                        summary(firstWheelModRelief)$coeff[3,1],
                                        summary(firstWheelModRelief)$coeff[4,1],
                                        summary(firstWheelModRelief)$coeff[5,1],
                                        summary(firstWheelModRelief)$coeff[6,1],
                                        summary(firstWheelModRelief)$coeff[7,1],
                                        summary(firstWheelModSad)$coeff[2,1],
                                        summary(firstWheelModSad)$coeff[3,1],
                                        summary(firstWheelModSad)$coeff[4,1],
                                        summary(firstWheelModSad)$coeff[5,1],
                                        summary(firstWheelModSad)$coeff[6,1],
                                        summary(firstWheelModSad)$coeff[7,1],
                                        summary(firstWheelModDisapp)$coeff[2,1],
                                        summary(firstWheelModDisapp)$coeff[3,1],
                                        summary(firstWheelModDisapp)$coeff[4,1],
                                        summary(firstWheelModDisapp)$coeff[5,1],
                                        summary(firstWheelModDisapp)$coeff[6,1],
                                        summary(firstWheelModDisapp)$coeff[7,1],
                                        summary(firstWheelModRegret)$coeff[2,1],
                                        summary(firstWheelModRegret)$coeff[3,1],
                                        summary(firstWheelModRegret)$coeff[4,1],
                                        summary(firstWheelModRegret)$coeff[5,1],
                                        summary(firstWheelModRegret)$coeff[6,1],
                                        summary(firstWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(firstWheelModHappy)$coeff[2,2],
                                        summary(firstWheelModHappy)$coeff[3,2],
                                        summary(firstWheelModHappy)$coeff[4,2],
                                        summary(firstWheelModHappy)$coeff[5,2],
                                        summary(firstWheelModHappy)$coeff[6,2],
                                        summary(firstWheelModHappy)$coeff[7,2],
                                        summary(firstWheelModContent)$coeff[2,2],
                                        summary(firstWheelModContent)$coeff[3,2],
                                        summary(firstWheelModContent)$coeff[4,2],
                                        summary(firstWheelModContent)$coeff[5,2],
                                        summary(firstWheelModContent)$coeff[6,2],
                                        summary(firstWheelModContent)$coeff[7,2],
                                        summary(firstWheelModRelief)$coeff[2,2],
                                        summary(firstWheelModRelief)$coeff[3,2],
                                        summary(firstWheelModRelief)$coeff[4,2],
                                        summary(firstWheelModRelief)$coeff[5,2],
                                        summary(firstWheelModRelief)$coeff[6,2],
                                        summary(firstWheelModRelief)$coeff[7,2],
                                        summary(firstWheelModSad)$coeff[2,2],
                                        summary(firstWheelModSad)$coeff[3,2],
                                        summary(firstWheelModSad)$coeff[4,2],
                                        summary(firstWheelModSad)$coeff[5,2],
                                        summary(firstWheelModSad)$coeff[6,2],
                                        summary(firstWheelModSad)$coeff[7,2],
                                        summary(firstWheelModDisapp)$coeff[2,2],
                                        summary(firstWheelModDisapp)$coeff[3,2],
                                        summary(firstWheelModDisapp)$coeff[4,2],
                                        summary(firstWheelModDisapp)$coeff[5,2],
                                        summary(firstWheelModDisapp)$coeff[6,2],
                                        summary(firstWheelModDisapp)$coeff[7,2],
                                        summary(firstWheelModRegret)$coeff[2,2],
                                        summary(firstWheelModRegret)$coeff[3,2],
                                        summary(firstWheelModRegret)$coeff[4,2],
                                        summary(firstWheelModRegret)$coeff[5,2],
                                        summary(firstWheelModRegret)$coeff[6,2],
                                        summary(firstWheelModRegret)$coeff[7,2])
                              )

secondWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("Second",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(secondWheelModHappy)$coeff[2,1],
                                        summary(secondWheelModHappy)$coeff[3,1],
                                        summary(secondWheelModHappy)$coeff[4,1],
                                        summary(secondWheelModHappy)$coeff[5,1],
                                        summary(secondWheelModHappy)$coeff[6,1],
                                        summary(secondWheelModHappy)$coeff[7,1],
                                        summary(secondWheelModContent)$coeff[2,1],
                                        summary(secondWheelModContent)$coeff[3,1],
                                        summary(secondWheelModContent)$coeff[4,1],
                                        summary(secondWheelModContent)$coeff[5,1],
                                        summary(secondWheelModContent)$coeff[6,1],
                                        summary(secondWheelModContent)$coeff[7,1],
                                        summary(secondWheelModRelief)$coeff[2,1],
                                        summary(secondWheelModRelief)$coeff[3,1],
                                        summary(secondWheelModRelief)$coeff[4,1],
                                        summary(secondWheelModRelief)$coeff[5,1],
                                        summary(secondWheelModRelief)$coeff[6,1],
                                        summary(secondWheelModRelief)$coeff[7,1],
                                        summary(secondWheelModSad)$coeff[2,1],
                                        summary(secondWheelModSad)$coeff[3,1],
                                        summary(secondWheelModSad)$coeff[4,1],
                                        summary(secondWheelModSad)$coeff[5,1],
                                        summary(secondWheelModSad)$coeff[6,1],
                                        summary(secondWheelModSad)$coeff[7,1],
                                        summary(secondWheelModDisapp)$coeff[2,1],
                                        summary(secondWheelModDisapp)$coeff[3,1],
                                        summary(secondWheelModDisapp)$coeff[4,1],
                                        summary(secondWheelModDisapp)$coeff[5,1],
                                        summary(secondWheelModDisapp)$coeff[6,1],
                                        summary(secondWheelModDisapp)$coeff[7,1],
                                        summary(secondWheelModRegret)$coeff[2,1],
                                        summary(secondWheelModRegret)$coeff[3,1],
                                        summary(secondWheelModRegret)$coeff[4,1],
                                        summary(secondWheelModRegret)$coeff[5,1],
                                        summary(secondWheelModRegret)$coeff[6,1],
                                        summary(secondWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(secondWheelModHappy)$coeff[2,2],
                                        summary(secondWheelModHappy)$coeff[3,2],
                                        summary(secondWheelModHappy)$coeff[4,2],
                                        summary(secondWheelModHappy)$coeff[5,2],
                                        summary(secondWheelModHappy)$coeff[6,2],
                                        summary(secondWheelModHappy)$coeff[7,2],
                                        summary(secondWheelModContent)$coeff[2,2],
                                        summary(secondWheelModContent)$coeff[3,2],
                                        summary(secondWheelModContent)$coeff[4,2],
                                        summary(secondWheelModContent)$coeff[5,2],
                                        summary(secondWheelModContent)$coeff[6,2],
                                        summary(secondWheelModContent)$coeff[7,2],
                                        summary(secondWheelModRelief)$coeff[2,2],
                                        summary(secondWheelModRelief)$coeff[3,2],
                                        summary(secondWheelModRelief)$coeff[4,2],
                                        summary(secondWheelModRelief)$coeff[5,2],
                                        summary(secondWheelModRelief)$coeff[6,2],
                                        summary(secondWheelModRelief)$coeff[7,2],
                                        summary(secondWheelModSad)$coeff[2,2],
                                        summary(secondWheelModSad)$coeff[3,2],
                                        summary(secondWheelModSad)$coeff[4,2],
                                        summary(secondWheelModSad)$coeff[5,2],
                                        summary(secondWheelModSad)$coeff[6,2],
                                        summary(secondWheelModSad)$coeff[7,2],
                                        summary(secondWheelModDisapp)$coeff[2,2],
                                        summary(secondWheelModDisapp)$coeff[3,2],
                                        summary(secondWheelModDisapp)$coeff[4,2],
                                        summary(secondWheelModDisapp)$coeff[5,2],
                                        summary(secondWheelModDisapp)$coeff[6,2],
                                        summary(secondWheelModDisapp)$coeff[7,2],
                                        summary(secondWheelModRegret)$coeff[2,2],
                                        summary(secondWheelModRegret)$coeff[3,2],
                                        summary(secondWheelModRegret)$coeff[4,2],
                                        summary(secondWheelModRegret)$coeff[5,2],
                                        summary(secondWheelModRegret)$coeff[6,2],
                                        summary(secondWheelModRegret)$coeff[7,2])
                              )


bothWheelModGraphDF = data.frame(Emotion = factor(c(rep("Happy",6),rep("Content",6),rep("Relief",6),
                                                     rep("Sad",6),rep("Disappointed",6),rep("Regret",6)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              CoefficientType = factor(rep(c("Win", "PE", "absPE", 
                                                             "Win", "PE", "absPE"),6),
                                                       levels=c("Win", "PE", "absPE")),
                              EmotionForWhichWheel = rep("Both",36),
                              FirstWheel = factor(rep(c("Yes","Yes","Yes","No","No","No"),6),
                                                  levels=c("Yes","No")),
                              Value = c(summary(bothWheelModHappy)$coeff[2,1],
                                        summary(bothWheelModHappy)$coeff[3,1],
                                        summary(bothWheelModHappy)$coeff[4,1],
                                        summary(bothWheelModHappy)$coeff[5,1],
                                        summary(bothWheelModHappy)$coeff[6,1],
                                        summary(bothWheelModHappy)$coeff[7,1],
                                        summary(bothWheelModContent)$coeff[2,1],
                                        summary(bothWheelModContent)$coeff[3,1],
                                        summary(bothWheelModContent)$coeff[4,1],
                                        summary(bothWheelModContent)$coeff[5,1],
                                        summary(bothWheelModContent)$coeff[6,1],
                                        summary(bothWheelModContent)$coeff[7,1],
                                        summary(bothWheelModRelief)$coeff[2,1],
                                        summary(bothWheelModRelief)$coeff[3,1],
                                        summary(bothWheelModRelief)$coeff[4,1],
                                        summary(bothWheelModRelief)$coeff[5,1],
                                        summary(bothWheelModRelief)$coeff[6,1],
                                        summary(bothWheelModRelief)$coeff[7,1],
                                        summary(bothWheelModSad)$coeff[2,1],
                                        summary(bothWheelModSad)$coeff[3,1],
                                        summary(bothWheelModSad)$coeff[4,1],
                                        summary(bothWheelModSad)$coeff[5,1],
                                        summary(bothWheelModSad)$coeff[6,1],
                                        summary(bothWheelModSad)$coeff[7,1],
                                        summary(bothWheelModDisapp)$coeff[2,1],
                                        summary(bothWheelModDisapp)$coeff[3,1],
                                        summary(bothWheelModDisapp)$coeff[4,1],
                                        summary(bothWheelModDisapp)$coeff[5,1],
                                        summary(bothWheelModDisapp)$coeff[6,1],
                                        summary(bothWheelModDisapp)$coeff[7,1],
                                        summary(bothWheelModRegret)$coeff[2,1],
                                        summary(bothWheelModRegret)$coeff[3,1],
                                        summary(bothWheelModRegret)$coeff[4,1],
                                        summary(bothWheelModRegret)$coeff[5,1],
                                        summary(bothWheelModRegret)$coeff[6,1],
                                        summary(bothWheelModRegret)$coeff[7,1]),
                              CI = 1.96* c(summary(bothWheelModHappy)$coeff[2,2],
                                        summary(bothWheelModHappy)$coeff[3,2],
                                        summary(bothWheelModHappy)$coeff[4,2],
                                        summary(bothWheelModHappy)$coeff[5,2],
                                        summary(bothWheelModHappy)$coeff[6,2],
                                        summary(bothWheelModHappy)$coeff[7,2],
                                        summary(bothWheelModContent)$coeff[2,2],
                                        summary(bothWheelModContent)$coeff[3,2],
                                        summary(bothWheelModContent)$coeff[4,2],
                                        summary(bothWheelModContent)$coeff[5,2],
                                        summary(bothWheelModContent)$coeff[6,2],
                                        summary(bothWheelModContent)$coeff[7,2],
                                        summary(bothWheelModRelief)$coeff[2,2],
                                        summary(bothWheelModRelief)$coeff[3,2],
                                        summary(bothWheelModRelief)$coeff[4,2],
                                        summary(bothWheelModRelief)$coeff[5,2],
                                        summary(bothWheelModRelief)$coeff[6,2],
                                        summary(bothWheelModRelief)$coeff[7,2],
                                        summary(bothWheelModSad)$coeff[2,2],
                                        summary(bothWheelModSad)$coeff[3,2],
                                        summary(bothWheelModSad)$coeff[4,2],
                                        summary(bothWheelModSad)$coeff[5,2],
                                        summary(bothWheelModSad)$coeff[6,2],
                                        summary(bothWheelModSad)$coeff[7,2],
                                        summary(bothWheelModDisapp)$coeff[2,2],
                                        summary(bothWheelModDisapp)$coeff[3,2],
                                        summary(bothWheelModDisapp)$coeff[4,2],
                                        summary(bothWheelModDisapp)$coeff[5,2],
                                        summary(bothWheelModDisapp)$coeff[6,2],
                                        summary(bothWheelModDisapp)$coeff[7,2],
                                        summary(bothWheelModRegret)$coeff[2,2],
                                        summary(bothWheelModRegret)$coeff[3,2],
                                        summary(bothWheelModRegret)$coeff[4,2],
                                        summary(bothWheelModRegret)$coeff[5,2],
                                        summary(bothWheelModRegret)$coeff[6,2],
                                        summary(bothWheelModRegret)$coeff[7,2])
                              )


wheelModGraphDF = rbind(firstWheelModGraphDF, secondWheelModGraphDF, bothWheelModGraphDF)
wheelModGraphDF$EmotionForWhichWheel = factor(wheelModGraphDF$EmotionForWhichWheel,
                                              levels=c("First", "Second", "Both"))

p2 = ggplot(wheelModGraphDF, aes(x=CoefficientType, fill=FirstWheel, y=Value)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Value-CI, ymax=Value+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  ggtitle("2pm wheel shown first") +
  facet_grid(EmotionForWhichWheel ~ Emotion) + xlab("Coeff type") + ylab("Value of coeff") + my_default_theme

wheelModGraphDF$timeOfFirstWheel = "2pm"
wheelModGraphDF = rbind(wheelModGraphDF_earlier, wheelModGraphDF)
wheelModGraphDF$timeOfFirstWheel = factor(wheelModGraphDF$timeOfFirstWheel, levels=c("10am", "2pm"))

wheelModGraphDF$combined = factor((wheelModGraphDF$timeOfFirstWheel=="2pm") + 2*(wheelModGraphDF$FirstWheel=="No"), levels=c(0,1,2,3), labels = c("10amFirst,FirstWheelCoeff", "2pmFirst,FirstWheelCoeff", "10amFirst,SecondWheelCoeff", "2pmFirst,SecondWheelCoeff"))

p3 = ggplot(wheelModGraphDF, aes(x=CoefficientType, fill=combined, y=Value)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Value-CI, ymax=Value+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  facet_grid(EmotionForWhichWheel ~ Emotion) + xlab("Coeff type") + ylab("Value of coeff") + my_default_theme + theme(legend.position="top")

```

### Analysis on individual wheels

#### Subset by if later wheel is shown first

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy for first wheel, first wheel   | `r summary(firstWheelModHappy)$coefficients[1,1]` (**`r summary(firstWheelModHappy)$coefficients[1,3]`**) | `r summary(firstWheelModHappy)$coefficients[2,1]` (**`r summary(firstWheelModHappy)$coefficients[2,3]`**)        | `r summary(firstWheelModHappy)$coefficients[3,1]` (**`r summary(firstWheelModHappy)$coefficients[3,3]`**)       | `r summary(firstWheelModHappy)$coefficients[4,1]` (`r summary(firstWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModHappy)$coefficients[5,1]` (`r summary(firstWheelModHappy)$coefficients[5,3]`)        | `r summary(firstWheelModHappy)$coefficients[6,1]` (`r summary(firstWheelModHappy)$coefficients[6,3]`)       | `r summary(firstWheelModHappy)$coefficients[7,1]` (`r summary(firstWheelModHappy)$coefficients[7,3]`)
Happy for second wheel, coeffs on first wheel   | `r summary(secondWheelModHappy)$coefficients[1,1]` (**`r summary(secondWheelModHappy)$coefficients[1,3]`**) | `r summary(secondWheelModHappy)$coefficients[2,1]` (`r summary(secondWheelModHappy)$coefficients[2,3]`)        | `r summary(secondWheelModHappy)$coefficients[3,1]` (`r summary(secondWheelModHappy)$coefficients[3,3]`)       | `r summary(secondWheelModHappy)$coefficients[4,1]` (`r summary(secondWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModHappy)$coefficients[5,1]` (**`r summary(secondWheelModHappy)$coefficients[5,3]`**)        | `r summary(secondWheelModHappy)$coefficients[6,1]` (**`r summary(secondWheelModHappy)$coefficients[6,3]`**)       | `r summary(secondWheelModHappy)$coefficients[7,1]` (`r summary(secondWheelModHappy)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Content for first wheel, first wheel   | `r summary(firstWheelModContent)$coefficients[1,1]` (**`r summary(firstWheelModContent)$coefficients[1,3]`**) | `r summary(firstWheelModContent)$coefficients[2,1]` (**`r summary(firstWheelModContent)$coefficients[2,3]`**)        | `r summary(firstWheelModContent)$coefficients[3,1]` (**`r summary(firstWheelModContent)$coefficients[3,3]`**)       | `r summary(firstWheelModContent)$coefficients[4,1]` (`r summary(firstWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModContent)$coefficients[5,1]` (**`r summary(firstWheelModContent)$coefficients[5,3]`**)        | `r summary(firstWheelModContent)$coefficients[6,1]` (`r summary(firstWheelModContent)$coefficients[6,3]`)       | `r summary(firstWheelModContent)$coefficients[7,1]` (`r summary(firstWheelModContent)$coefficients[7,3]`)
Content for second wheel, coeffs on first wheel   | `r summary(secondWheelModContent)$coefficients[1,1]` (**`r summary(secondWheelModContent)$coefficients[1,3]`**) | `r summary(secondWheelModContent)$coefficients[2,1]` (**`r summary(secondWheelModContent)$coefficients[2,3]`**)        | `r summary(secondWheelModContent)$coefficients[3,1]` (`r summary(secondWheelModContent)$coefficients[3,3]`)       | `r summary(secondWheelModContent)$coefficients[4,1]` (`r summary(secondWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModContent)$coefficients[5,1]` (**`r summary(secondWheelModContent)$coefficients[5,3]`**)        | `r summary(secondWheelModContent)$coefficients[6,1]` (**`r summary(secondWheelModContent)$coefficients[6,3]`**)       | `r summary(secondWheelModContent)$coefficients[7,1]` (`r summary(secondWheelModContent)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Relief for first wheel, coeffs on first wheel   | `r summary(firstWheelModRelief)$coefficients[1,1]` (**`r summary(firstWheelModRelief)$coefficients[1,3]`**) | `r summary(firstWheelModRelief)$coefficients[2,1]` (`r summary(firstWheelModRelief)$coefficients[2,3]`)        | `r summary(firstWheelModRelief)$coefficients[3,1]` (**`r summary(firstWheelModRelief)$coefficients[3,3]`**)       | `r summary(firstWheelModRelief)$coefficients[4,1]` (`r summary(firstWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModRelief)$coefficients[5,1]` (`r summary(firstWheelModRelief)$coefficients[5,3]`)        | `r summary(firstWheelModRelief)$coefficients[6,1]` (`r summary(firstWheelModRelief)$coefficients[6,3]`)       | `r summary(firstWheelModRelief)$coefficients[7,1]` (`r summary(firstWheelModRelief)$coefficients[7,3]`)
Relief for second wheel, coeff on first wheel   | `r summary(secondWheelModRelief)$coefficients[1,1]` (**`r summary(secondWheelModRelief)$coefficients[1,3]`**) | `r summary(secondWheelModRelief)$coefficients[2,1]` (`r summary(secondWheelModRelief)$coefficients[2,3]`)        | `r summary(secondWheelModRelief)$coefficients[3,1]` (`r summary(secondWheelModRelief)$coefficients[3,3]`)       | `r summary(secondWheelModRelief)$coefficients[4,1]` (`r summary(secondWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModRelief)$coefficients[5,1]` (`r summary(secondWheelModRelief)$coefficients[5,3]`)        | `r summary(secondWheelModRelief)$coefficients[6,1]` (**`r summary(secondWheelModRelief)$coefficients[6,3]`**)       | `r summary(secondWheelModRelief)$coefficients[7,1]` (`r summary(secondWheelModRelief)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Sad for first wheel, coeffs on first wheel   | `r summary(firstWheelModSad)$coefficients[1,1]` (**`r summary(firstWheelModSad)$coefficients[1,3]`**) | `r summary(firstWheelModSad)$coefficients[2,1]` (**`r summary(firstWheelModSad)$coefficients[2,3]`**)        | `r summary(firstWheelModSad)$coefficients[3,1]` (**`r summary(firstWheelModSad)$coefficients[3,3]`**)       | `r summary(firstWheelModSad)$coefficients[4,1]` (**`r summary(firstWheelModSad)$coefficients[4,3]`**)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModSad)$coefficients[5,1]` (`r summary(firstWheelModSad)$coefficients[5,3]`)        | `r summary(firstWheelModSad)$coefficients[6,1]` (`r summary(firstWheelModSad)$coefficients[6,3]`)       | `r summary(firstWheelModSad)$coefficients[7,1]` (`r summary(firstWheelModSad)$coefficients[7,3]`)
Sad for second wheel, coeff on first wheel   | `r summary(secondWheelModSad)$coefficients[1,1]` (**`r summary(secondWheelModSad)$coefficients[1,3]`**) | `r summary(secondWheelModSad)$coefficients[2,1]` (`r summary(secondWheelModSad)$coefficients[2,3]`)        | `r summary(secondWheelModSad)$coefficients[3,1]` (`r summary(secondWheelModSad)$coefficients[3,3]`)       | `r summary(secondWheelModSad)$coefficients[4,1]` (`r summary(secondWheelModSad)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModSad)$coefficients[5,1]` (**`r summary(secondWheelModSad)$coefficients[5,3]`**)        | `r summary(secondWheelModSad)$coefficients[6,1]` (**`r summary(secondWheelModSad)$coefficients[6,3]`**)       | `r summary(secondWheelModSad)$coefficients[7,1]` (**`r summary(secondWheelModSad)$coefficients[7,3]`**)
--- | --- | --- | --- | ---
Disapp for first wheel, coeffs on first wheel   | `r summary(firstWheelModDisapp)$coefficients[1,1]` (**`r summary(firstWheelModDisapp)$coefficients[1,3]`**) | `r summary(firstWheelModDisapp)$coefficients[2,1]` (`r summary(firstWheelModDisapp)$coefficients[2,3]`)        | `r summary(firstWheelModDisapp)$coefficients[3,1]` (**`r summary(firstWheelModDisapp)$coefficients[3,3]`**)       | `r summary(firstWheelModDisapp)$coefficients[4,1]` (**`r summary(firstWheelModDisapp)$coefficients[4,3]`**)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModDisapp)$coefficients[5,1]` (`r summary(firstWheelModDisapp)$coefficients[5,3]`)        | `r summary(firstWheelModDisapp)$coefficients[6,1]` (`r summary(firstWheelModDisapp)$coefficients[6,3]`)       | `r summary(firstWheelModDisapp)$coefficients[7,1]` (`r summary(firstWheelModDisapp)$coefficients[7,3]`)
Disapp for second wheel, coeff on first wheel   | `r summary(secondWheelModDisapp)$coefficients[1,1]` (**`r summary(secondWheelModDisapp)$coefficients[1,3]`**) | `r summary(secondWheelModDisapp)$coefficients[2,1]` (`r summary(secondWheelModDisapp)$coefficients[2,3]`)        | `r summary(secondWheelModDisapp)$coefficients[3,1]` (`r summary(secondWheelModDisapp)$coefficients[3,3]`)       | `r summary(secondWheelModDisapp)$coefficients[4,1]` (`r summary(secondWheelModDisapp)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModDisapp)$coefficients[5,1]` (**`r summary(secondWheelModDisapp)$coefficients[5,3]`**)        | `r summary(secondWheelModDisapp)$coefficients[6,1]` (**`r summary(secondWheelModDisapp)$coefficients[6,3]`**)       | `r summary(secondWheelModDisapp)$coefficients[7,1]` (`r summary(secondWheelModDisapp)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Regret for first wheel, first wheel   | `r summary(firstWheelModRegret)$coefficients[1,1]` (**`r summary(firstWheelModRegret)$coefficients[1,3]`**) | `r summary(firstWheelModRegret)$coefficients[2,1]` (`r summary(firstWheelModRegret)$coefficients[2,3]`)        | `r summary(firstWheelModRegret)$coefficients[3,1]` (**`r summary(firstWheelModRegret)$coefficients[3,3]`**)       | `r summary(firstWheelModRegret)$coefficients[4,1]` (`r summary(firstWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(firstWheelModRegret)$coefficients[5,1]` (`r summary(firstWheelModRegret)$coefficients[5,3]`)        | `r summary(firstWheelModRegret)$coefficients[6,1]` (`r summary(firstWheelModRegret)$coefficients[6,3]`)       | `r summary(firstWheelModRegret)$coefficients[7,1]` (`r summary(firstWheelModRegret)$coefficients[7,3]`)
Regret for second wheel, coeff on first wheel   | `r summary(secondWheelModRegret)$coefficients[1,1]` (**`r summary(secondWheelModRegret)$coefficients[1,3]`**) | `r summary(secondWheelModRegret)$coefficients[2,1]` (`r summary(secondWheelModRegret)$coefficients[2,3]`)        | `r summary(secondWheelModRegret)$coefficients[3,1]` (`r summary(secondWheelModRegret)$coefficients[3,3]`)       | `r summary(secondWheelModRegret)$coefficients[4,1]` (`r summary(secondWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(secondWheelModRegret)$coefficients[5,1]` (**`r summary(secondWheelModRegret)$coefficients[5,3]`**)        | `r summary(secondWheelModRegret)$coefficients[6,1]` (**`r summary(secondWheelModRegret)$coefficients[6,3]`**)       | `r summary(secondWheelModRegret)$coefficients[7,1]` (`r summary(secondWheelModRegret)$coefficients[7,3]`)







### Overall emotion

#### later wheel shown first

If we now look at the overall emotion attributed

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy overall, coeffs on first wheel   | `r summary(bothWheelModHappy)$coefficients[1,1]` (**`r summary(bothWheelModHappy)$coefficients[1,3]`**) | `r summary(bothWheelModHappy)$coefficients[2,1]` (**`r summary(bothWheelModHappy)$coefficients[2,3]`**)        | `r summary(bothWheelModHappy)$coefficients[3,1]` (`r summary(bothWheelModHappy)$coefficients[3,3]`)       | `r summary(bothWheelModHappy)$coefficients[4,1]` (`r summary(bothWheelModHappy)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModHappy)$coefficients[5,1]` (**`r summary(bothWheelModHappy)$coefficients[5,3]`**)        | `r summary(bothWheelModHappy)$coefficients[6,1]` (**`r summary(bothWheelModHappy)$coefficients[6,3]`**)       | `r summary(bothWheelModHappy)$coefficients[7,1]` (`r summary(bothWheelModHappy)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Content overall, coeffs on first wheel   | `r summary(bothWheelModContent)$coefficients[1,1]` (**`r summary(bothWheelModContent)$coefficients[1,3]`**) | `r summary(bothWheelModContent)$coefficients[2,1]` (**`r summary(bothWheelModContent)$coefficients[2,3]`**)        | `r summary(bothWheelModContent)$coefficients[3,1]` (`r summary(bothWheelModContent)$coefficients[3,3]`)       | `r summary(bothWheelModContent)$coefficients[4,1]` (`r summary(bothWheelModContent)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModContent)$coefficients[5,1]` (**`r summary(bothWheelModContent)$coefficients[5,3]`**)        | `r summary(bothWheelModContent)$coefficients[6,1]` (**`r summary(bothWheelModContent)$coefficients[6,3]`**)       | `r summary(bothWheelModContent)$coefficients[7,1]` (`r summary(bothWheelModContent)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Relief overall, coeffs on first wheel   | `r summary(bothWheelModRelief)$coefficients[1,1]` (**`r summary(bothWheelModRelief)$coefficients[1,3]`**) | `r summary(bothWheelModRelief)$coefficients[2,1]` (**`r summary(bothWheelModRelief)$coefficients[2,3]`**)        | `r summary(bothWheelModRelief)$coefficients[3,1]` (`r summary(bothWheelModRelief)$coefficients[3,3]`)       | `r summary(bothWheelModRelief)$coefficients[4,1]` (`r summary(bothWheelModRelief)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModRelief)$coefficients[5,1]` (`r summary(bothWheelModRelief)$coefficients[5,3]`)        | `r summary(bothWheelModRelief)$coefficients[6,1]` (**`r summary(bothWheelModRelief)$coefficients[6,3]`**)       | `r summary(bothWheelModRelief)$coefficients[7,1]` (`r summary(bothWheelModRelief)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Sad overall, coeffs on first wheel   | `r summary(bothWheelModSad)$coefficients[1,1]` (**`r summary(bothWheelModSad)$coefficients[1,3]`**) | `r summary(bothWheelModSad)$coefficients[2,1]` (**`r summary(bothWheelModSad)$coefficients[2,3]`**)        | `r summary(bothWheelModSad)$coefficients[3,1]` (`r summary(bothWheelModSad)$coefficients[3,3]`)       | `r summary(bothWheelModSad)$coefficients[4,1]` (`r summary(bothWheelModSad)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModSad)$coefficients[5,1]` (**`r summary(bothWheelModSad)$coefficients[5,3]`**)        | `r summary(bothWheelModSad)$coefficients[6,1]` (`r summary(bothWheelModSad)$coefficients[6,3]`)       | `r summary(bothWheelModSad)$coefficients[7,1]` (`r summary(bothWheelModSad)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Regret overall, coeffs on first wheel   | `r summary(bothWheelModRegret)$coefficients[1,1]` (**`r summary(bothWheelModRegret)$coefficients[1,3]`**) | `r summary(bothWheelModRegret)$coefficients[2,1]` (**`r summary(bothWheelModRegret)$coefficients[2,3]`**)        | `r summary(bothWheelModRegret)$coefficients[3,1]` (`r summary(bothWheelModRegret)$coefficients[3,3]`)       | `r summary(bothWheelModRegret)$coefficients[4,1]` (`r summary(bothWheelModRegret)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModRegret)$coefficients[5,1]` (**`r summary(bothWheelModRegret)$coefficients[5,3]`**)        | `r summary(bothWheelModRegret)$coefficients[6,1]` (`r summary(bothWheelModRegret)$coefficients[6,3]`)       | `r summary(bothWheelModRegret)$coefficients[7,1]` (`r summary(bothWheelModRegret)$coefficients[7,3]`)
--- | --- | --- | --- | ---
Disapp overall, coeffs on first wheel   | `r summary(bothWheelModDisapp)$coefficients[1,1]` (**`r summary(bothWheelModDisapp)$coefficients[1,3]`**) | `r summary(bothWheelModDisapp)$coefficients[2,1]` (**`r summary(bothWheelModDisapp)$coefficients[2,3]`**)        | `r summary(bothWheelModDisapp)$coefficients[3,1]` (`r summary(bothWheelModDisapp)$coefficients[3,3]`)       | `r summary(bothWheelModDisapp)$coefficients[4,1]` (`r summary(bothWheelModDisapp)$coefficients[4,3]`)
 (coeffs on second wheel)   | --- | `r summary(bothWheelModDisapp)$coefficients[5,1]` (**`r summary(bothWheelModDisapp)$coefficients[5,3]`**)        | `r summary(bothWheelModDisapp)$coefficients[6,1]` (`r summary(bothWheelModDisapp)$coefficients[6,3]`)       | `r summary(bothWheelModDisapp)$coefficients[7,1]` (`r summary(bothWheelModDisapp)$coefficients[7,3]`)



```{r v62-graphs-1, echo=FALSE, fig.height=6, fig.width=10}

p1
p2
p3

```



```{r echo=FALSE}

v62data$combinedWin = v62data$win_1 + v62data$win_2
v62data$combinedPE = v62data$PE_1 + v62data$PE_2
v62data$combinedAbsPE = v62data$absPE_1 + v62data$absPE_2

bothWheelModCombinedHappy   = lmer(happy3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
bothWheelModCombinedContent = lmer(content3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
bothWheelModCombinedRelief  = lmer(relief3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
bothWheelModCombinedSad     = lmer(sad3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
bothWheelModCombinedDisapp  = lmer(disapp3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
bothWheelModCombinedRegret  = lmer(regret3 ~ (combinedWin + combinedPE + combinedAbsPE) +
                           (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
```

If we make combined win, PE and absPE variables

Emotion (t value in parenthesis)          | Main Effect   | Coeff on Win  | Coeff on PE   | Coeff on absPE
-------------     | ------------- | ------------- | ------------- | -------------
Happy overall, combined vars   | `r summary(bothWheelModCombinedHappy)$coefficients[1,1]` (**`r summary(bothWheelModCombinedHappy)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedHappy)$coefficients[2,1]` (**`r summary(bothWheelModCombinedHappy)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedHappy)$coefficients[3,1]` (**`r summary(bothWheelModCombinedHappy)$coefficients[3,3]`**)       | `r summary(bothWheelModCombinedHappy)$coefficients[4,1]` (`r summary(bothWheelModCombinedHappy)$coefficients[4,3]`)
Content overall, combined vars   | `r summary(bothWheelModCombinedContent)$coefficients[1,1]` (**`r summary(bothWheelModCombinedContent)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedContent)$coefficients[2,1]` (**`r summary(bothWheelModCombinedContent)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedContent)$coefficients[3,1]` (`r summary(bothWheelModCombinedContent)$coefficients[3,3]`)       | `r summary(bothWheelModCombinedContent)$coefficients[4,1]` (`r summary(bothWheelModCombinedContent)$coefficients[4,3]`)
Relief overall, combined vars   | `r summary(bothWheelModCombinedRelief)$coefficients[1,1]` (**`r summary(bothWheelModCombinedRelief)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedRelief)$coefficients[2,1]` (**`r summary(bothWheelModCombinedRelief)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedRelief)$coefficients[3,1]` (`r summary(bothWheelModCombinedRelief)$coefficients[3,3]`)       | `r summary(bothWheelModCombinedRelief)$coefficients[4,1]` (`r summary(bothWheelModCombinedRelief)$coefficients[4,3]`)
--- | --- | --- | --- | ---
Sad overall, combined vars   | `r summary(bothWheelModCombinedSad)$coefficients[1,1]` (**`r summary(bothWheelModCombinedSad)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedSad)$coefficients[2,1]` (**`r summary(bothWheelModCombinedSad)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedSad)$coefficients[3,1]` (`r summary(bothWheelModCombinedSad)$coefficients[3,3]`)       | `r summary(bothWheelModCombinedSad)$coefficients[4,1]` (`r summary(bothWheelModCombinedSad)$coefficients[4,3]`)
Regret overall, combined vars   | `r summary(bothWheelModCombinedRegret)$coefficients[1,1]` (**`r summary(bothWheelModCombinedRegret)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedRegret)$coefficients[2,1]` (**`r summary(bothWheelModCombinedRegret)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedRegret)$coefficients[3,1]` (`r summary(bothWheelModCombinedRegret)$coefficients[3,3]`)       | `r summary(bothWheelModCombinedRegret)$coefficients[4,1]` (`r summary(bothWheelModCombinedRegret)$coefficients[4,3]`)
Disapp overall, combined vars   | `r summary(bothWheelModCombinedDisapp)$coefficients[1,1]` (**`r summary(bothWheelModCombinedDisapp)$coefficients[1,3]`**) | `r summary(bothWheelModCombinedDisapp)$coefficients[2,1]` (**`r summary(bothWheelModCombinedDisapp)$coefficients[2,3]`**)        | `r summary(bothWheelModCombinedDisapp)$coefficients[3,1]` (`r summary(bothWheelModCombinedDisapp)$coefficients[3,3]`)       | `r summary(bothWheelModCombinedDisapp)$coefficients[4,1]` (`r summary(bothWheelModCombinedDisapp)$coefficients[4,3]`)

```{r, echo=FALSE, fig.height=6, fig.width=10}

wheelModelHappy = lmer(happy3 ~ happy1 + happy2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
wheelModelContent = lmer(content3 ~ content1 + content2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
wheelModelRelief = lmer(relief3 ~ relief1 + relief2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
wheelModelSad = lmer(sad3 ~ sad1 + sad2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
wheelModelDisapp = lmer(disapp3 ~ disapp1 + disapp2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)
wheelModelRegret = lmer(regret3 ~ regret1 + regret2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data)


# summary(wheelModelHappy)
# summary(wheelModelContent)
# summary(wheelModelRelief)
# summary(wheelModelSad)
# summary(wheelModelDisapp)
# summary(wheelModelRegret)

#showEarlierWheelFirst

v62data_s1 = subset(v62data, v62data$showEarlierWheelFirst==1)

wheelModelHappy = lmer(happy3 ~ (happy1 + happy2) + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelContent = lmer(content3 ~ content1 + content2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRelief = lmer(relief3 ~ relief1 + relief2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelSad = lmer(sad3 ~ sad1 + sad2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelDisapp = lmer(disapp3 ~ disapp1 + disapp2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRegret = lmer(regret3 ~ regret1 + regret2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)

wheelModelGraphDF = data.frame(Emotion = factor(c(rep("Happy",2),rep("Content",2),rep("Relief",2),
                                                     rep("Sad",2),rep("Disappointed",2),rep("Regret",2)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              EmotionToWhichWheel = factor(rep(c("First","Second"),6),
                                                  levels=c("First","Second")),
                              earlierWheelShownFirst = rep(1,12),
                              Value = c(summary(wheelModelHappy)$coeff[2,1],
                                        summary(wheelModelHappy)$coeff[3,1],
                                        summary(wheelModelContent)$coeff[2,1],
                                        summary(wheelModelContent)$coeff[3,1],
                                        summary(wheelModelRelief)$coeff[2,1],
                                        summary(wheelModelRelief)$coeff[3,1],
                                        summary(wheelModelSad)$coeff[2,1],
                                        summary(wheelModelSad)$coeff[3,1],
                                        summary(wheelModelDisapp)$coeff[2,1],
                                        summary(wheelModelDisapp)$coeff[3,1],
                                        summary(wheelModelRegret)$coeff[2,1],
                                        summary(wheelModelRegret)$coeff[3,1]),
                              CI = 1.96* c(summary(wheelModelHappy)$coeff[2,2],
                                        summary(wheelModelHappy)$coeff[3,2],
                                        summary(wheelModelContent)$coeff[2,2],
                                        summary(wheelModelContent)$coeff[3,2],
                                        summary(wheelModelRelief)$coeff[2,2],
                                        summary(wheelModelRelief)$coeff[3,2],
                                        summary(wheelModelSad)$coeff[2,2],
                                        summary(wheelModelSad)$coeff[3,2],
                                        summary(wheelModelDisapp)$coeff[2,2],
                                        summary(wheelModelDisapp)$coeff[3,2],
                                        summary(wheelModelRegret)$coeff[2,2],
                                        summary(wheelModelRegret)$coeff[3,2])
                              )

#
# subset(wheelModelGraphDF, wheelModelGraphDF$EmotionToWhichWheel=="Second")$Value/subset(wheelModelGraphDF, wheelModelGraphDF$EmotionToWhichWheel=="First")$Value
# mean(subset(wheelModelGraphDF, wheelModelGraphDF$EmotionToWhichWheel=="Second")$Value/subset(wheelModelGraphDF, wheelModelGraphDF$EmotionToWhichWheel=="First")$Value)

v62data_s1 = subset(v62data, v62data$showEarlierWheelFirst==0)

wheelModelHappy = lmer(happy3 ~ (happy1 + happy2) + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelContent = lmer(content3 ~ content1 + content2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRelief = lmer(relief3 ~ relief1 + relief2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelSad = lmer(sad3 ~ sad1 + sad2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelDisapp = lmer(disapp3 ~ disapp1 + disapp2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRegret = lmer(regret3 ~ regret1 + regret2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)

wheelModelGraphDF2 = data.frame(Emotion = factor(c(rep("Happy",2),rep("Content",2),rep("Relief",2),
                                                     rep("Sad",2),rep("Disappointed",2),rep("Regret",2)),
                                               levels=c("Happy", "Content", "Relief", 
                                                        "Sad", "Disappointed", "Regret")),
                              EmotionToWhichWheel = factor(rep(c("First","Second"),6),
                                                  levels=c("First","Second")),
                              earlierWheelShownFirst = rep(0,12),
                              Value = c(summary(wheelModelHappy)$coeff[2,1],
                                        summary(wheelModelHappy)$coeff[3,1],
                                        summary(wheelModelContent)$coeff[2,1],
                                        summary(wheelModelContent)$coeff[3,1],
                                        summary(wheelModelRelief)$coeff[2,1],
                                        summary(wheelModelRelief)$coeff[3,1],
                                        summary(wheelModelSad)$coeff[2,1],
                                        summary(wheelModelSad)$coeff[3,1],
                                        summary(wheelModelDisapp)$coeff[2,1],
                                        summary(wheelModelDisapp)$coeff[3,1],
                                        summary(wheelModelRegret)$coeff[2,1],
                                        summary(wheelModelRegret)$coeff[3,1]),
                              CI = 1.96* c(summary(wheelModelHappy)$coeff[2,2],
                                        summary(wheelModelHappy)$coeff[3,2],
                                        summary(wheelModelContent)$coeff[2,2],
                                        summary(wheelModelContent)$coeff[3,2],
                                        summary(wheelModelRelief)$coeff[2,2],
                                        summary(wheelModelRelief)$coeff[3,2],
                                        summary(wheelModelSad)$coeff[2,2],
                                        summary(wheelModelSad)$coeff[3,2],
                                        summary(wheelModelDisapp)$coeff[2,2],
                                        summary(wheelModelDisapp)$coeff[3,2],
                                        summary(wheelModelRegret)$coeff[2,2],
                                        summary(wheelModelRegret)$coeff[3,2])
                              )

# # note that I switched the ordering of the "First" and "Second"
# subset(wheelModelGraphDF2, wheelModelGraphDF2$EmotionToWhichWheel=="First")$Value/subset(wheelModelGraphDF2, wheelModelGraphDF2$EmotionToWhichWheel=="Second")$Value
# mean(subset(wheelModelGraphDF2, wheelModelGraphDF2$EmotionToWhichWheel=="First")$Value/subset(wheelModelGraphDF2, wheelModelGraphDF2$EmotionToWhichWheel=="Second")$Value)

wheelModelGraphCombDF = rbind(wheelModelGraphDF, wheelModelGraphDF2)
wheelModelGraphCombDF$earlierWheelShownFirst = factor(wheelModelGraphCombDF$earlierWheelShownFirst,
                                                  levels=c(1,0),
                                                  labels=c("Congruent", "Incongruent"))

ggplot(wheelModelGraphCombDF, aes(x=earlierWheelShownFirst, fill=EmotionToWhichWheel, y=Value)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") +
  geom_errorbar(aes(ymin=Value-CI, ymax=Value+CI), size=.3, width=.2, position=position_dodge(.9)) + 
  scale_fill_brewer(palette="Set2", name="WheelEmotion", breaks=c("First", "Second"), labels=c("FirstWheel", "SecondWheel")) +
  facet_wrap( ~ Emotion) + xlab("Evidence Order") + ylab("Value of Coefficient") + my_default_theme +
  theme(legend.position = "top")


v62data_s1 = v62data #subset(v62data, v62data$showEarlierWheelFirst==1)

wheelModelHappy = lmer(happy3 ~ (happy1 + happy2) + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelContent = lmer(content3 ~ content1 + content2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRelief = lmer(relief3 ~ relief1 + relief2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelSad = lmer(sad3 ~ sad1 + sad2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelDisapp = lmer(disapp3 ~ disapp1 + disapp2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)
wheelModelRegret = lmer(regret3 ~ regret1 + regret2 + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_s1)


```

If 10am wheel is shown first, then the second emotion attributed (2pm wheel) weighs a lot more in the overall emotion attributed (Left set of bars).

If 2pm wheel is shown first, the first emotion attributed (2pm wheel) still matters more than the 10am emotion for Happy, Content, Sad, but to a lesser extent, and for Relief, Disappointed and Regret, there seems to be no difference.





If we now use the emotions from the first two wheels to predict overall emotion, collapsed across both temporal orders,

Emotion (t value in parenthesis)          | Main Effect   | Coeff on first wheel emotion  | Coeff on second wheel emotion
-------------     | ------------- | ------------- | ------------- 
Happy overall   | `r summary(wheelModelHappy)$coefficients[1,1]` (**`r summary(wheelModelHappy)$coefficients[1,3]`**) | `r summary(wheelModelHappy)$coefficients[2,1]` (**`r summary(wheelModelHappy)$coefficients[2,3]`**)        | `r summary(wheelModelHappy)$coefficients[3,1]` (**`r summary(wheelModelHappy)$coefficients[3,3]`**)
Content overall   | `r summary(wheelModelContent)$coefficients[1,1]` (**`r summary(wheelModelContent)$coefficients[1,3]`**) | `r summary(wheelModelContent)$coefficients[2,1]` (**`r summary(wheelModelContent)$coefficients[2,3]`**)        | `r summary(wheelModelContent)$coefficients[3,1]` (**`r summary(wheelModelContent)$coefficients[3,3]`**)
Relief overall   | `r summary(wheelModelRelief)$coefficients[1,1]` (**`r summary(wheelModelRelief)$coefficients[1,3]`**) | `r summary(wheelModelRelief)$coefficients[2,1]` (**`r summary(wheelModelRelief)$coefficients[2,3]`**)        | `r summary(wheelModelRelief)$coefficients[3,1]` (**`r summary(wheelModelRelief)$coefficients[3,3]`**)
Sad overall   | `r summary(wheelModelSad)$coefficients[1,1]` (**`r summary(wheelModelSad)$coefficients[1,3]`**) | `r summary(wheelModelSad)$coefficients[2,1]` (**`r summary(wheelModelSad)$coefficients[2,3]`**)        | `r summary(wheelModelSad)$coefficients[3,1]` (**`r summary(wheelModelSad)$coefficients[3,3]`**)
Disapp overall   | `r summary(wheelModelDisapp)$coefficients[1,1]` (**`r summary(wheelModelDisapp)$coefficients[1,3]`**) | `r summary(wheelModelDisapp)$coefficients[2,1]` (**`r summary(wheelModelDisapp)$coefficients[2,3]`**)        | `r summary(wheelModelDisapp)$coefficients[3,1]` (**`r summary(wheelModelDisapp)$coefficients[3,3]`**)
Regret overall   | `r summary(wheelModelRegret)$coefficients[1,1]` (**`r summary(wheelModelRegret)$coefficients[1,3]`**) | `r summary(wheelModelRegret)$coefficients[2,1]` (**`r summary(wheelModelRegret)$coefficients[2,3]`**)        | `r summary(wheelModelRegret)$coefficients[3,1]` (**`r summary(wheelModelRegret)$coefficients[3,3]`**)


```{r v62-overall-emotion-model-stats, echo=FALSE}
v62data_s1 = subset(v62data, v62data$showEarlierWheelFirst==1)

# Stat tests: use a restricted-full model comparison across all emotions.
v62data_melt = melt(v62data_s1, id.vars = c("workerid", "spinnerID_1", "spinnerID_2"),
                    measure.vars = c("happy1", "content1", "relief1", "sad1", "disapp1", "regret1"),
                    variable.name = "Emotion", value.name="Emotion1")
v62data_melt$Emotion2 = melt(v62data_s1, id.vars = c("workerid", "spinnerID_1", "spinnerID_2"),
                    measure.vars = c("happy2", "content2", "relief2", "sad2", "disapp2", "regret2"),
                    variable.name = "Emotion", value.name="Emotion2")$Emotion2
v62data_melt$Emotion3 = melt(v62data_s1, id.vars = c("workerid", "spinnerID_1", "spinnerID_2"),
                    measure.vars = c("happy3", "content3", "relief3", "sad3", "disapp3", "regret3"),
                    variable.name = "Emotion", value.name="Emotion3")$Emotion3
v62data_melt$Emotion = factor(v62data_melt$Emotion, levels = c("happy1", "content1", "relief1",
                                                               "sad1", "disapp1", "regret1"),
                              labels = c("Happy", "Content", "Relief", "Sad", "Disapp", "Regret"))

v62data_melt$Emotion12 = v62data_melt$Emotion1 + v62data_melt$Emotion2

wheelModelFull = lmer(Emotion3 ~ (Emotion12 + Emotion2)*Emotion + (1|Emotion) + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_melt)
# summary(wheelModelFull)
wheelModelFullr = lmer(Emotion3 ~ (Emotion12)*Emotion + (1|Emotion) + (1|spinnerID_1) + (1|spinnerID_2) + (1|workerid), v62data_melt)
# summary(wheelModelFullr)
anova(wheelModelFull, wheelModelFullr)

```
